Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-09 Paper/paper.tex
Background Section edits

\subsection{Availability}
Web applications are available anywhere there's internet. There is rarely need to install anything on a given device. Due to the ever-increasing popularity of mobile devices, most applications have both mobile and full versions of their software and so the application is ``with'' the user at all times. This instant and continuous availability means that users only have to know how to use a web browser in order to access the application.

A recent push in the web application community is toward offline versions of applications that merely cache changes until the user can connect to the internet once again and all changes are pushed online. This increases the availability of web applications even further.

\subsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality and in this day and age all devices come equipped with browsers that should have no problems. This also means that the developer need not, generally, worry about hardware configurations, conflicting software, and other problems that can arise in desktop applications.

@@

As the web is being increasingly used on mobile devices, HTML5 also introduces geolocation functionality. This functionality requires user approval, but once that approval is gained, the web application has access to a rough idea of where the user is located. When used on devices that have GPS, such as phones and tablets, this area is more defined and a stronger lock on the user's position can be obtained. This geolocation functionality has opened the door for brand new types of web applications that can much more closely tie in with what the user is seeing or the area that they are in. For example, advertisements can be more targeted or an application can display distances to nearby points of interest.

@@

So now that the client has been clarified, what is the client-side portion of an application? The client-side portion interacts with the browser to request assets from the server and then displaying them in a human-readable way. The client-side also deals with the user interface and interactivity of a web page, e.g., the client-side displays a web form, the client fills in the information and clicks ``submit'' and the client-side packages up the data and sends it to the server-side.

@@

Clients communicate with the Server through a request-response architecture. Clients send a request to the server, sometimes with information attached, such as a form submittal or login, and the server returns a response with either a success/failure message, or additional data.

One example of a client-server architecture that is popular for the web is Representational State Transfer, also known as REST, architecture. If a client-server architecture meets all of the REST criteria, it is said to be RESTful. As this paper is not about Client Server interactions, we will not outline the constraints but instead outline how RESTful APIs look in web applications. The RESTful web APIs use: 1) a base URI, 2) an internet media type, and 3) the standard HTTP methods.

A base URI is simple, in the context of a web application, it is just a URL such as ``http://myrestapi.com/entities''.

@@

The standard HTTP methods are GET, PUT, POST, and DELETE. These methods define what the request is intending to do. For example, a GET request sent to ``http://myrestapi.com/entities'' would tell the server that the client wants to get information regarding all entities. A PUT request would tell the server that the client wishes to replace the entire entity collection with another collection that would be sent along with the request. A POST request would tell the server to create a new entity in the collection. Finally, a DELETE request would tell the server to delete the entities. The four methods take on slightly different, but very similar meanings when used with specific element URIs, such as ``http://myrestapi.com/entities/entity1''. A GET request asks the server for a displayable version of the entity and the client then displays it. A PUT request asks the server to replace the existing entity or create an entire new entity if one does not exist. A POST request is generally not used as that implies that this single entity is itself a collection. A DELETE request asks the server to remove this entity.

An important part of being a RESTful API is that any change to a web page or element is done through a hypertext link and all actions on an element share a single URI. For example, all updates to ``entity1'' are done through ``http://myrestapi.com/entities/entity1'' using the various HTTP methods that can be called using hypertext links on the page. Compare this to a different way to handle functionality such as ``http://myrestapi.com/entities/UpdateEntity'' where the HTTP request contains information regarding the entity to update and all updates, regardless of which entity is changing, go through a single URI.

@@

There are a number of different types of tests and testing concepts, we will just focus on Unit Testing, Integration Testing, Continuous Integration, and Acceptance Testing.

\subsection{Unit Testing}
Unit testing is the testing of specific functions and functionality, or ``test units.'' According to IEEE, test units are ``A set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures that satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.'' \cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

In the above example there are two modules, Word and Sentence. Unit Testing the Word is relatively simple because it is self-contained and only runs functions on the string given to it. Unit Testing the Sentence module is tougher because of it's reliance on Words. The goal of a good set of Unit Tests is to test as much of a module as possible in isolation from all other modules. This includes interactions between modules. In our example, testing the wordCount function is a Unit Test because none of the Word functionality is actually required. The other methods of Sentence pose a problem because of their need to call Word functions. Although there are ways to Unit Test those functions, that is beyond the scope of this overview and would only serve to confuse the reader.

@@

\subsection{Integration Testing}
After writing Unit tests, a developer writes Integration tests. Integration tests are used to determine if modules work together to produce correct results. In our previous example, this would mean testing most of the Sentence functions to ensure that they properly use the Words that the Sentence contains. Integration Tests cover a wider variety of test situations from single methods to entire modules.

>>>>

\subsection{Availability}
Web applications are available anywhere there's internet\footnote{A recent push in the web application community is toward offline versions of applications that merely cache changes until the user can connect to the internet once again and all changes are pushed online. This increases the availability of web applications even further.}. There is rarely need to install anything on a given device. Due to the ever-increasing popularity of mobile devices, most applications have both mobile and full versions of their software and so the application is ``with'' the user at all times. This instant and continuous availability means that users only have to know how to use a web browser in order to access the application.

\subsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality. Nearly all devices made today come equipped with browsers that support the necessary functionality. This also means that the developer need not, generally, worry about hardware configurations, conflicting software, and other problems that can arise in desktop applications.

@@

As the web is being increasingly used on mobile devices, HTML5 also introduces geolocation functionality. This functionality requires user approval, but once that approval is gained, the web application has access to a rough area in which the user is located. When used on devices that have GPS, such as phones and tablets, this area is more defined and the user's position can be obtained more reliably and accurately. This geolocation functionality has opened the door for brand new types of web applications that can more closely tie in with what the user is seeing or the area that they are in. For example, advertisements can be more targeted or an application can display distances to nearby points of interest.

@@

The client-side portion of an application interacts with the browser to request assets from the server and then displaying them in a human-readable way. The client-side also deals with the user interface and interactivity of a web page, e.g., the client-side displays a web form, the client fills in the information and clicks ``submit'' and the client-side packages up the data and sends it to the server.

@@

Clients communicate with the Server through a request-response architecture. Clients send a request to the server, often with information attached, such as a form submittal or login, and the server returns a response with either a success/failure message, or additional data.

One example of a client-server architecture that is popular for the web is the Representational State Transfer, also known as REST, architecture. If a client-server architecture meets all of the REST criteria, it is said to be RESTful. As this paper is not about Client Server interactions, we will not outline the constraints but instead outline how RESTful APIs look in web applications. The RESTful web APIs use: 1) a base URI, 2) an internet media type, and 3) the standard HTTP methods.

A base URI is simple; in the context of a web application, it is just a URL such as ``http://myrestapi.com/entities''.

@@

The standard HTTP methods are GET, PUT, POST, and DELETE. These methods define what the request is intending to do. For example, a GET request sent to ``http://myrestapi.com/entities'' would indicate to the server that the client wants to get information regarding all entities. A PUT request would indicate that the client wishes to replace the entire entity collection with another collection that would be sent along with the request. A POST request would ask the server to create a new entity in the collection. Finally, a DELETE request would tell the server to delete the entities. The four methods take on slightly different, but very similar meanings when used with specific element URIs, such as ``http://myrestapi.com/entities/entity1''. A GET request asks the server for a displayable version of the entity and the client then displays it. A PUT request asks the server to replace the existing entity or create an entire new entity if one does not exist. A POST request is generally not used as that implies that this single entity is itself a collection. A DELETE request asks the server to remove this entity.

An important part of being a RESTful API is that any change to a web page or element is done through a hypertext link and all actions on an element share a single URI. For example, all updates to ``entity1'' are done through ``http://myrestapi.com/entities/entity1'' using the various HTTP methods that can be called using hypertext links on the page. Compare this to a different way to handle that functionality such as ``http://myrestapi.com/entities/UpdateEntity'' where the HTTP request contains information regarding the entity to update. This method handles all updates, regardless of which entity is changing, through a single URI.

@@

There are a number of different types of tests and testing concepts. We will focus on Unit Testing, Integration Testing, Continuous Integration, and Acceptance Testing.

\subsection{Unit Testing}
Unit testing is the testing of specific functions and functionality, or ``test units.'' According to IEEE, test units are ``[a] set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures that satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.'' \cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

In the above example there are two modules, \lstinline{Word} and \lstinline{Sentence}. Unit Testing the \lstinline{Word} is relatively simple because it is self-contained and only runs functions on the string given to it. Unit Testing the \lstinline{Sentence} module is tougher because of its reliance on \lstinline{Word}s. The goal of a good set of Unit Tests is to test as much of a module as possible in isolation from all other modules. This includes interactions between modules. In our example, testing the \lstinline{wordCount} function is a Unit Test because none of the \lstinline{Word} functionality is actually required. The other methods of \lstinline{Sentence} pose a problem because of their need to call \lstinline{Word} functions. Although there are ways to Unit Test those functions, that is beyond the scope of this overview and would only serve to confuse the reader.

@@

\subsection{Integration Testing}
After writing Unit tests, a developer writes Integration tests. Integration tests are used to determine if modules work together to produce correct results. In our previous example, this would mean testing most of the \lstinline{Sentence} functions to ensure that they properly use the \lstinline{Word}s that the \lstinline{Sentence} contains. Integration Tests cover a wider variety of test situations from single methods to entire modules.
